Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{{DISTRIBUTION STATEMENT A. Approved for public release.} }

### 2021-05-15 paper/related-work.tex
Pass on related work

>>>>

Data-flow semantics are well studied \cite{10.1145/41625.41641,97300, 10.1145/1379023.1375674,10.1145/2345141.2248426,10.1007/978-3-540-45212-6_10}. State machine semantics can be added to synchronous data-flow \cite{10.1145/1086228.1086261}. The idea is to translate imperative constructs into equivalent synchronous data flow constructs. The resulting Lustre can them be compiled to target a platform. The goal is to provide a seamless connection between pure data-flow and pure control design.

There is a fully verified compiler that takes Lustre and turns it into a binary executable \cite{10.1145/3140587.3062358}. The first compilation pass turns synchronous data-flow in Lustre to assembly. The compilation is specified and verified in Coq. The key is in combining infinite sequences of data-flow models with incremental manipulation of memories akin to an imperative model. CompCert is used on the backend to create the final rendered executable.
